%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy CV/Resume
% XeLaTeX Template
% Version 1.0 (5/5/2014)
%
% Original author:
% Debarghya Das (http://www.debarghyadas.com)
% With extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[letterpaper]{cv} % Use US Letter paper, change to a4paper for A4
\usepackage{enumitem}
\begin{document}

% ----------------------------------------------------------------------------------------
%	TITLE SECTION
% ----------------------------------------------------------------------------------------
\lastupdated
% Print the Last Updated text at the top right

\namesection{Jacob}{Chvatal}{ % Your name
  \urlstyle{same}\url{https://jacob.chvatal.com} | \urlstyle{same}\url{https://github.com/jakeisnt} \\ % Your website, LinkedIn profile or other web address
  \href{mailto:chvatal.j@northeastern.edu}{chvatal.j@northeastern.edu} | +1 503.330.8568 % Your contact information
}

% ----------------------------------------------------------------------------------------
%	LEFT COLUMN
% ----------------------------------------------------------------------------------------
\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

  % ------------------------------------------------
  % Education
  % ------------------------------------------------
  \section{Education}
  \subsection{Northeastern University}
  \descript{B.S. in Computer Science}
  \location{Expected Dec. 2022 | Boston, MA}
  Khoury College of Computer Sciences \\
  Dean's List (Fall 2018, Spring 2019) \\
  \location{ GPA:\@ 3.53 / 4.0}
  \sectionspace % Some whitespace after the section

  % ------------------------------------------------
  % Links
  % ------------------------------------------------
  \section{Links}
  \begin{tabular}[t]{lll}
  GitHub &\href{https://github.com/jakeisnt}{\bf jakeisnt} \\
  LinkedIn &\href{https://www.linkedin.com/in/jacob-chvatal}{\bf jacob-chvatal} \\
  Twitter &\href{https://twitter.com/jakeissnt}{\bf @jakeissnt} \\
  Website &\href{https://jacob.chvatal.com}{\bf jacob.chvatal.com} \\
  \end{tabular}
  \sectionspace

  % ------------------------------------------------
  % Coursework
  % ------------------------------------------------
  \section{Coursework}
  Networks \\
  Computer Systems \\
  Artificial Intelligence \\
  Theory of Computation \\
  Compilers \\
  Programming Languages \\
  Computer-Aided Reasoning \\
  Fundamentals of CS 1 (TAx3) \\
  Fundamentals of CS 2 (TAx1) \\
  Algorithms \\
  Research

  \sectionspace

  % ------------------------------------------------
  % Skills
  % ------------------------------------------------

  \section{Skills}
  \subsection{Web}
  \textbullet{} JavaScript/TypeScript \\
  \textbullet{} React/NextJS, Webpack, Bundling \\
  \textbullet{} Clojure/ClojureScript \\
  \sectionspace
  \subsection{Infrastructure}
  \textbullet{} Linux: Debian+, Arch+, NixOS \\
  \textbullet{}Shell (bash, zsh), Nix flakes \\
  \textbullet{} Docker, Docker-Compose, Kubernetes \\

  \sectionspace
  \subsection{Interpersonal}
  \textbullet{} UI accessibility standards proficient \\
  \textbullet{} CI organization and infrastructure \\
  \textbullet{} AGILE project management and loeadership \\

  \sectionspace
  \subsection{Research}
  Interests: Programming language development,
  teaching, agency in computing, formal verification \\
  \textbullet{} Lisp: Racket, ACL2/s \\
  \textbullet{} ML: OCaml, Coq, Rust, Haskell \\
  \sectionspace

  % ----------------------------------------------------------------------------------------
\end{minipage} % The end of the left column
\hfill
%
% ----------------------------------------------------------------------------------------
%	RIGHT COLUMN
% ----------------------------------------------------------------------------------------
%
\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page

  % ------------------------------------------------
  % Experience
  % ------------------------------------------------
  \section{Experience}
  \runsubsection{Skira Tech}
  \descript{| Software Engineering Intern}
  \location{August 2020 – December 2020 | Stockholm, Sweden}
  \vspace{\topsep} % hacky fix for awkward extra vertical space
  \begin{tightitemize}
    \item Developed a marketplace to transform the Swedish grain industry with GraphQL, Sequelize, PostgreSQL, React/Redux.
    \item Spearheaded and executed significant contributions to the product, reworking the central user interface and enhancing application performance.
  \end{tightitemize}
  \sectionspace

  % ------------------------------------------------
  \runsubsection{Intel Corporation}
  \descript{| Software Engineering Intern}
  \location{May 2020 – August 2020 | Hillsboro, OR}
  \begin{tightitemize}
    \item Designed and developed a multimodal data management service for the Edge Insights video analytics system with Python, Protobuf and Docker (+compose).
    \item Interfaced with VDMS graph database; containerized and hosted.
  \end{tightitemize}
  \sectionspace

  % ------------------------------------------------
  \runsubsection{CDK Global}
  \descript{| Software Development Intern}

  \location{June 2018 – Aug 2018 | Portland, OR}
  \begin{tightitemize}
    \item Led development of React \& Spring Boot web app w/ Material UI components
    \item Utilized Docker and nginx to containerize and host application through CDK
  \end{tightitemize}
  \sectionspace

  % ------------------------------------------------
  \runsubsection{Portland State University}
  \descript{| Student Intern}

  \location{June 2017 – Aug 2017 | Portland, OR}
  \begin{tightitemize}
    \item Impl. C++ library to compress and apply linear algebra to sparse matrix data
    \item Applied matrix operations to analyze and graph large 3D mesh structures
    \item Distr.`\ code to COEUS supercluster w/ OpenMP parallel programming pragmas
  \end{tightitemize}

  % ------------------------------------------------
  % Research
  % ------------------------------------------------
  \section{Research}

  \runsubsection{NU Sandbox}
  \descript{| Developer and Project Lead}

  \location{May 2019 – August 2021 | Boston, MA}
  \begin{tightitemize}
    \item Reworked A-Eye, a website used by a course at NEU to teach ML/AI
    \item Managed team for a CV app to analyze ELISA vials for chem.`\ experiments
    \item Used Python's Kivy framework, Android's JDK and OpenCV
    \item Founded GraduateNU, a schedule planning system for NEU students
  \end{tightitemize}

  % ------------------------------------------------
  % Projects
  % ------------------------------------------------
  \section{Projects}

  \runsubsection{Functional Compiler}
  \location{OCaml}
  Developed a compiler targeting x86 Assembly for a functional language with type checking, inference, garbage collection, and  I/O for a capstone course.
  \sectionspace

  \runsubsection{Web Infrastructure}
  \location{Ongoing}
  Designing a distributed system and corresponding design language, leveraging NixOS, Org-mode, and various life-tracking tools to maintain a peronal search engine, wiki, and analytics API, leveraging Rust, Clojure, NextJS, CI, and NixOps.
  \sectionspace

  \runsubsection{System Configuration}
  \location{NixOS}
  Developed a completely reproducible NixOS configuration EDSL with innovative technologies like Wayland and Pipewire. Configured self-hosted server infrastructure. Enabled practically instant reinstallation and redeployment.\@ \sectionspace

  \runsubsection{Coursework}
  \location{Northeastern}
  A responsive shell and FUSE-based file system in C,
  interpreters for many toy languages in Haskell,
  a substantial compiler for a typed functional programming language in OCaml and much more. \\
  \textit{Code for these projects is available upon request as per Northeastern policy.}

  % ----------------------------------------------------------------------------------------
\end{minipage} % The end of the right column
\end{document}
