%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy CV/Resume
% XeLaTeX Template
% Version 1.0 (5/5/2014)
%
% Original author:
% Debarghya Das (http://www.debarghyadas.com)
% With extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[letterpaper]{deedy-resume} % Use US Letter paper, change to a4paper for A4 
\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------
\lastupdated % Print the Last Updated text at the top right

\namesection{Jacob}{Chvatal}{ % Your name
\urlstyle{same}\url{https://jacob.chvatal.com} \\ % Your website, LinkedIn profile or other web address
\href{mailto:chvatal.j@northeastern.edu}{chvatal.j@northeastern.edu} | 503.330.8568 % Your contact information
}

%----------------------------------------------------------------------------------------
%	LEFT COLUMN
% ----------------------------------------------------------------------------------------
\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

%------------------------------------------------
% Education
%------------------------------------------------
\section{Education}
\subsection{Northeastern University}
\descript{BS in Computer Science}
\location{Expected May 2022 | Boston, MA}
Khoury College of Computer Sciences \\
Dean's List (All Semesters) \\
\location{ Cum. GPA: 3.92 / 4.0 \\
Major GPA: 3.94 / 4.0}
\sectionspace % Some whitespace after the section

%------------------------------------------------
\subsection{Westview High School}
\location{Grad. June 2018 | Portland, Oregon}
Nat AP Scholar | Nat. Merit Finalist
\sectionspace % Some whitespace after the section

%------------------------------------------------
% Links
%------------------------------------------------
\section{Links}
Github:// \href{https://github.com/jakechv}{\bf jakechv} \\
LinkedIn:// \href{https://www.linkedin.com/in/jacob-chvatal}{\bf jacob-chvatal} \\
Twitter:// \href{https://twitter.com/jakechvatal}{\bf @jakechvatal} \\
\sectionspace % Some whitespace after the section

%------------------------------------------------
% Coursework
%------------------------------------------------
\section{Coursework}
\subsection{Graduate}
Algorithms
\sectionspace % Some whitespace after the section

%------------------------------------------------
\subsection{Undergraduate}
Artificial Intelligence \\
Computer Systems \\
Theory of Computation \\
Programming Languages \\
Compilers
\sectionspace % Some whitespace after the section

%------------------------------------------------
% Skills
%------------------------------------------------

\section{Skills}

\subsection{Programming}

\location{Over 5000 lines:}
Java \textbullet{} Shell \textbullet{} JavaScript \textbullet{} Haskell \\
OCaml \textbullet{} Python \textbullet{} React  \\

\location{Over 1000 lines:}
C \textbullet{} C++ \textbullet{} CSS \textbullet{} MySQL \textbullet{} Assembly \\

\location{Familiar:}
PostgreSQL \textbullet{} Android \textbullet{} SQLite \textbullet{} \LaTeX\ \\

\sectionspace % Some whitespace after the section

\subsection{Technologies}

\location{Experienced:}
(Arch/Debian) Linux  \textbullet{} Docker  \\

\location{Familiar:}
NixOS \textbullet{} Plan9 \textbullet{} SQLite \\

\sectionspace % Some whitespace after the section

%----------------------------------------------------------------------------------------
\subsection{Environments}

% \location{Experienced:}
Emacs \textbullet{} (Neo)Vim \textbullet{} Visual Studio Code \\
\textbullet{} IntelliJ IDEA \textbullet{} tmux \textbullet{} Microsoft Suite \\
\textbullet{} Adobe Suite

%----------------------------------------------------------------------------------------
\end{minipage} % The end of the left column
\hfill
%
%----------------------------------------------------------------------------------------
%	RIGHT COLUMN
%----------------------------------------------------------------------------------------
%
\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page

%------------------------------------------------
% Experience
%------------------------------------------------
\section{Experience}
\runsubsection{Skira Tech}
\descript{| Software Engineering Intern}

\location{Expected August 2020 – Dec 2020 | Stockholm, Sweden}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
\item Writing React code.
\end{tightitemize}

\sectionspace % Some whitespace after the section
%------------------------------------------------
\runsubsection{Intel Corporation}
\descript{| Software Engineering Intern}

\location{May 2020 – August 2020 | Hillsboro, OR}
\begin{tightitemize}
\item Writing Python code.
\end{tightitemize}

\sectionspace % Some whitespace after the section
%------------------------------------------------
\runsubsection{CDK Global}
\descript{| Software Developnent Intern}

\location{June 2018 – Aug 2018 | Portland, OR}
\begin{tightitemize}
  \item Led development of React \& Spring Boot web app w/ Material UI components
  \item Utilized Docker and nginx to containerize and host application through CDK
  \item Practiced Agile/Scrum methodologies through Atlassian Jira, Confluence, Stash
\end{tightitemize}

\sectionspace % Some whitespace after the section
% ------------------------------------------------
\runsubsection{Portland State University}
\descript{| Student Intern}

\location{June 20217 – Aug 2017 | Portland, OR}
\begin{tightitemize}
  \item Impl. C++ library to compress and apply linear algebra to sparse matrix data
  \item Applied matrix operations to analyze and graph large 3D mesh structures
  \item Distr. code to COEUS supercluster w/ OpenMP parallel programming pragmas
\end{tightitemize}

\sectionspace % Some whitespace after the section

% ------------------------------------------------
% Research
%------------------------------------------------
\section{Research}

\runsubsection{NU Sandbox}
\descript{| Developer and Project Lead}

\location{May 2019 - Present | Boston, MA}

\sectionspace % Some whitespace after the section

% ------------------------------------------------
% Projects
% ------------------------------------------------
\section{Projects}
\runsubsection{Poo-NU}
\location{HackHarvard}
Assembled React Native application with Google Maps API,
GraphQL and MySQL to help students locate the nearest bathroom
on Northeastern's campus.
\sectionspace

\runsubsection{Dotfiles}
\location{Linux}
Always iterating on a custom system configuration for my Arch Linux system. \\
Involves substantial work with shell scripting, VimScript and Emacs Lisp.
\sectionspace

\runsubsection{Coursework}
\location{Northeastern}
I've worked on lots of school projects -- including several games in ISL/Java,
a shell and FUSE-based file system in C,
a quiz sharing application with Python's Flask and SQL,
interpreters for many toy languages in Haskell,
and a substantial compiler for a typed functional programming language in OCaml. \\
\textit{Code for these projects is available upon request as per Northeastern policy.}
\sectionspace

% ------------------------------------------------
% Other Employment
%------------------------------------------------
\section{Other Employment}
\runsubsection{Northeastern University}
\descript{| CS 'Fundies' 1 and 2 Tutor}

\location{Jan 2019 - May 2020 | Boston, MA}
Taught introductory functional programming concepts, data structures and \\
OOP paradigms in Racket's ISL and Java with advanced content.
\begin{tightitemize}
\item Held office hours and weekly lab sessions for assignments and concepts.
\item Evaluated homework for students weekly for form and function of programs.
\end{tightitemize}

\sectionspace % Some whitespace after the section

% ----------------------------------------------------------------------------------------
\end{minipage} % The end of the right column
\end{document}
