%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for CV/Resume
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%

%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, letterpaper]{awesome-cv}
% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}
% Specify the location of the included fonts
\fontdir[fonts/]
% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-red}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you dont want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

%-------------------------------------------------------------------------------
%	personal information
%	comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% available options: circle|rectangle,edge/noedge,left/right
% \photo[rectangle,edge,right]{./examples/profile}
\name{jacob}{chvatal}
\position{software architect{\enskip\cdotp\enskip}security expert}
\address{42-8, bangbae-ro 15-gil, seocho-gu, seoul, 00681, rep. of korea}

\mobile{(+82) 10-9030-1843}
\email{posquit0.bj@gmail.com}
\homepage{www.posquit0.com}
\github{posquit0}
\linkedin{posquit0}
% \gitlab{gitlab-id}
% \stackoverflow{so-id}{so-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \medium{madium-id}
% \googlescholar{googlescholar-id}{name-to-display}
%% \firstname and \lastname will be used
% \googlescholar{googlescholar-id}{}
% \extrainfo{extra informations}

%-------------------------------------------------------------------------------
\begin{document}
\title{ - Resume}
Jacob Chvatal
Computational Designer
github: jakeisnt
linkedin: jacob-chvatal

\begin{cvparagraph} Formally trained engineer and self-taught product designer. I am passionate about the intersection of technology and the creative arts, in all its forms.
Born, raised, and currently residing in the San Francisco Bay Area. Willing to relocate.
\end{cvparagraph}

\cvsection{Work}
\begin{cventries}
\cventroo{Uber\newline Design Engineer\newline Feb. 2018 to Present}{
\begin{cvitems}
\item{ Designed and built a suite of tools to help a team of 300+ designers do their best work. Involved in all stages of the product development process, from concept to mock to production code.}
\item{ Contributor to Base, the Uber design system, powering experiences seen by millions worldwide.}\end{cvitems}}
\cventroo{Uber\newline Software Engineering Intern\newline May 2017 - August 2017}{
\begin{cvitems}
Growth and internal tools. Helped create improvements to the Uber driver signup flow, increasing UberMOTO registrations in Jakarta, Indonesia by 3 pct.\end{cvitems}}
\cventroo{Chartbeat\newline Software Engineering Intern\newline June 2016 - Dec. 2016}{
\begin{cvitems}
\item{ Front-end engineer at a 75 person startup.}
\item{ Created a "trending topic" discovery tool, helping attract and retain clients (e.g. New York Times, the Atlantic, CNN). Contributed to core product redesign using React and Angular.}\end{cvitems}}\end{cventries}
\cvsection{Education}
\begin{cventries}
\cventroo{UC Berkeley\newline BA, Computer Science\newline 2014-2017\newline 3.3 GPA}{
\begin{cvitems}
HCI emphasis. Extracirricular highlights include:
\item{ Teaching front-end web development at Cal Hacks, the worlds largest collegiate hackathon}
\item{ Leading design for Hackers@Berkeley, the worlds largest STEM organization. Marketed and promoted weekly events with as many as 1,000 attendees.}
\item{ Creating a zine with lyrics generated by a recurrent neurla network}
\item{ Creating a protest communication network post-2016 election, sending alerts to 500+ students daily}
\item{ Writing a viral investigative article about "white student unions", receiving worldwide press coverage (NYT, CBC ancouver, Washington Post, etc.)}
\item{ Prototyping a text input system for the Microsoft Hololens using Framer and Unity}\end{cvitems}}\end{cventries}
\cvsection{Skills}
\begin{cventries}
\cventroo{Design Tools
}{
\begin{cvitems}
Figma + Sketch + Adobe Creative Suite + Framer\end{cvitems}}

\cventroo{Programming Languages + Frameworks
}{
\begin{cvitems}
6+ years of experience in web development (React, Node, Angular). Familiar with mobile (Android + iOS) environments as well as prototyping in Unity.\end{cvitems}}
\end{cventries}


\end{document}